---
title: "jw_team_form"
author: "John"
date: "10/4/2019"
output: slidy_presentation
runtime: shiny
---

```{r setup, include=FALSE}
```

# Slider 1

## Slider 2

## Slider 3

## Slider 4            User Manuel for Shiny Interactive APP
This App is a database App. To start to use this App, there are four entries.

In the box provided, you are to respond to the question by typing your details.

We created four textInput in the ui.R, that will request the user to input text asked and then the input will be reply by the server.r
Below are the way to use the app:

Sidebar with reactive input
- At the prompt type the answer to the question.

- Use the drop down to select your age.

- click to add and then look at the right hand side of the app to see your entry
Whenever a field is filled, it will aggregate all data
from the form which is a reactive function

- You can search or sort what you have added by typing the correct name entry.
it will render all the date that has been added to the database of the form.


##     Slider 4 Shiny Interative APP
```{r,echo=FALSE}

library(shiny)
fields <- c("name","age","address","contact")

ui <- fluidPage(
  
  titlePanel("JW Team Form"),
  
  sidebarLayout(
    sidebarPanel(
      textInput("name","Your Name"),
      selectInput("age","Age bracket",c("18-25","25-45","above 45")),
      textInput("address","Please enter your address"),
      textInput("contact","Please enter your contact"),
      actionButton("save","Add")
      
    ),
    
    mainPanel(
      mainPanel(
        
        DT::dataTableOutput("responses", width = 500), tags$hr()
        
      )
    )
  )
)

library(shiny)
server <- function(input, output,session) {

  saveData <- function(data) {
    data <- as.data.frame(t(data))
    if (exists("responses")) {
      responses <<- rbind(responses, data)
    } else {
      responses <<- data
    }
  }
  
  loadData <- function() {
    if (exists("responses")) {
      responses
    }
  }
  
  formData <- reactive({
    data <- sapply(fields, function(x) input[[x]])
    data
  })
  
  observeEvent(input$save, {
    saveData(formData())
  })
  
  output$responses <- DT::renderDataTable({
    input$save
    loadData()
  })     
}

shinyApp(ui, server)
```


##   slider 5 Scatter Plot

```{r, comment="",fig.align='center',fig.cap="Graph With Code Display"}
plot(mtcars$mpg, mtcars$hp, xlab = "Mile per Gallon", ylab = "Hourse-power")
```


